---
title: "ecoocc"
output:
    md_document
---


# ecoocc
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/KevCaz/ecoocc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KevCaz/ecoocc/actions/workflows/R-CMD-check.yaml)

A Rcpp implementation of various computations done on presence/absence
matrices.



## Installation

The simplest way to install this packages is to use the [`remotes`](https://CRAN.R-project.org/package=remotes) package


```R
install.package("remotes")
remotes::install_github("KevCaz/ecoocc")
```

Once installed, load it and try it!

```{r}
library(ecoocc)
```


## What is implemented so far?

### Presence absence matrix 

`ec_as_pa()` creates objects of class `pa`, there is a shortcut to randomly  generate  object of class `pa` quickly, `ec_generate_pa()`. 


```{r, results = "hold"}
# a pa object of 10 and 5 species all species having a prensence probability of .4
ec_generate_pa(10, 5, .4)
```


### Beta diversity

```{r, results = "hold"}
(mat <- ec_generate_pa(5, 3, .5))
ec_betadiversity(mat)
```


### Rarefaction

```{r, results = "hold"}
(mat <- ec_generate_pa(10, 4, .4))
ec_rarefaction(mat, 6)
```


### Temporal beta diversity


```{r, results = "hold"}
(mat <- rbind(c(0,0,1), c(0,1,0)))
ec_cooc_count_pair(mat)
 ```


### Occurrence

```{r, results = "hold"}
mat <- rbind(c(0,0,1), c(0,1,0))
ec_cooc_count_pair(mat)
 ```
